Phylogenetics

### 2023-05-15 episodes/phylogenetics.Rmd
Refined phylogenetics. Complete draft of mol epi

For this exercise, we'll use the R package 
[`ape`](https://emmanuelparadis.github.io/) , which you should
install if it's not present on your setup:

>>>>

The exercise is done for a large part with pen and paper, and then a 
demonstration in R. We'll also use the R package 
[`ape`](https://emmanuelparadis.github.io/) , which you should
install if it's not present on your setup:
